Clustering Constraints on the Relative Sizes of Central and Satellite Galaxies

### 2017-11-26 paper/galsize_paper.tex
edited abstract and conclusions

\begin{abstract}
Using new SDSS measurements of projected galaxy clustering, $\wproj(\rproj),$ we place empirical constraints on the connection between galaxy size and halo virial radius.  
We find that small galaxies cluster much more strongly than large galaxies of the same stellar mass. 
The magnitude of this clustering difference increases on small scales, and decreases with stellar mass. Using {\tt Halotools} to forward model the observations, we test a simple empirical model in which present-day galaxy size is proportional to the size of the virial radius at the time the halo reached its maximum mass. This simple model reproduces the observed size-dependence of $\wproj(\rproj)$ in striking detail. 
The success of this model provides strong support for the conclusion that satellite galaxies have smaller sizes relative to central galaxies of the same halo mass. 
Our findings indicate that satellite size is set prior to the time of infall, and that a remarkably simple, linear size--virial radius relation emerges from the complex physics regulating galaxy size. 
We make quantitative predictions for future measurements of galaxy-galaxy lensing, including dependence upon size, scale, and stellar mass, and provide a simple scaling relation that can be used to calibrate hydrodynamical simulations and semi-analytic models. 
\end{abstract}

@@

\ben
\item Small galaxies cluster more strongly than large galaxies of the same stellar mass. Differences between the clustering of small and large galaxies increase on small scales $\rproj\lesssim1\mpc,$ and decrease with stellar mass (see Figure \ref{fig:rvir_only_clustering_absolute}). 
\item The most important factor influencing the clustering signal is the relative size of central and satellite galaxies. The magnitude, scale-dependence, and $\mstar-$dependence of $\rhalf-$dependent clustering provides strong evidence that satellite galaxies are smaller than central galaxies of the same halo mass.
\item A simple empirical model in which $\rhalf$ is proportional to halo $\rvir$ at the time when halo mass reached its maximum reproduces the size-dependence of SDSS galaxy clustering in striking detail (see Figure \ref{fig:clustering_ratio_upshot}). 
\item Models in which $\rhalf$ is regulated by $\mstar,$ rather than $\mhalo,$ are grossly discrepant with the observed $\wproj(\rproj),$ even when accounting for satellite mass stripping (see Figure \ref{fig:mstarmodelclustering}).
\item Taken together, our findings indicate that satellite-specific processes play a sub-dominant role in setting the different sizes of centrals and satellites; these size differences instead appear to be largely predetermined at the time of satellite infall.
\item The $\rvir$-based size model that reproduces the observed $\wproj(\rproj)$ makes an unambiguous  prediction for future observations of galaxy-galaxy lensing: for $\mstar-$selected samples, $\Delta\Sigma$ should be much stronger for small galaxies relative to large (see Figure \ref{fig:lensingprediction}). The strength of the predicted difference in $\Delta\Sigma$ makes this test well within reach of numerous present-day imaging surveys. 
\een

@@

\section*{Appendix: Treatment of Disrupted Subhalos}

@@

@@

%---------------------------------------------------------------------------------------------------
\begin{figure}
\centering
\includegraphics[width=8cm]{FIGS/orphan_satellite_fraction.pdf}
\caption{
{\bf Impact of orphans on $\fsat.$} The y-axis shows the fraction of galaxies that are not centrals, plotted as a function of stellar mass $\mstar.$ Different curves show results for three different choices for the treatment of disrupted subhalos, as indicated in the legend and described in the text of the appendix. 
}
\label{fig:orphan_satellite_fractions}
\end{figure}
%-----------------------------------------------------------------------------------------------------

>>>>

\begin{abstract}
Using new measurements of projected two-point correlation function, $\wproj(\rproj)$, of  the Sloan Digital Sky Survey galaxies of different sizes and stellar masses,
 we place empirical constraints on the connection between galaxy size and halo virial radius.  
We find that small galaxies cluster much more strongly than large galaxies of the same stellar mass. 
The magnitude of this clustering difference increases on small scales, and decreases with increasing stellar mass. 
Using {\tt Halotools} to forward model the observations, we test a simple empirical model in which present-day galaxy size is 
proportional to the size of the virial radius at the time the halo reached its maximum mass. This simple model reproduces the 
observed size-dependence of $\wproj(\rproj)$ in striking detail. 
The success of this model provides strong support for the conclusion that satellite galaxies have smaller sizes relative to central 
galaxies of the same halo mass. 
Our findings indicate that satellite size is set prior to the time of infall, and that a remarkably simple, linear size--virial radius relation 
emerges from the complex physics regulating galaxy size. 
We make quantitative predictions for future measurements of galaxy-galaxy lensing, including dependence upon size, scale, 
and stellar mass, and provide a simple scaling relation of the ratio of mean sizes of satellites and central galaxies as a function of their halo mass 
that can be used to calibrate hydrodynamical simulations and semi-analytic models. 
\end{abstract}

@@

\ben
\item Small galaxies cluster more strongly than large galaxies of the same stellar mass. Differences between the clustering of small and large galaxies increase on small scales $\rproj\lesssim1\mpc,$ and decrease with increasing stellar mass (see Figure \ref{fig:rvir_only_clustering_absolute}). 
\item The most important factor influencing the clustering signal is the relative size of central and satellite galaxies. The magnitude, scale-dependence, and $\mstar-$dependence of $\rhalf-$dependent clustering provides strong evidence that satellite galaxies are smaller than central galaxies of the same halo mass.
\item A simple empirical model in which $\rhalf$ is proportional to halo $\rvir$ at the time when halo mass reached its maximum reproduces the size-dependence of SDSS galaxy clustering in striking detail (see Figure \ref{fig:clustering_ratio_upshot}). 
\item Models in which $\rhalf$ is regulated by $\mstar,$ rather than $\mhalo,$ are grossly discrepant with the observed $\wproj(\rproj),$ even when accounting for satellite mass stripping (see Figure \ref{fig:mstarmodelclustering}).
\item Taken together, our findings indicate that satellite-specific processes play a sub-dominant role in setting the different sizes of centrals and satellites; the sizes of satelitte galaxies instead appear to be largely predetermined at the time of their infall.
\item The $\rvir$-based size model that reproduces the observed $\wproj(\rproj)$ makes an unambiguous  prediction for future observations of galaxy-galaxy lensing: for $\mstar-$selected samples, $\Delta\Sigma$ should be much stronger for small galaxies relative to large (see Figure \ref{fig:lensingprediction}). The strength of the predicted difference in $\Delta\Sigma$ makes this test well within reach of numerous present-day imaging surveys. 
\een

@@

\newpage
\section*{Appendix: Treatment of Disrupted Subhalos}

%---------------------------------------------------------------------------------------------------

@@

\begin{figure}
\centering
\includegraphics[width=8cm]{FIGS/orphan_satellite_fraction.pdf}
\caption{
{\bf Impact of orphans on $\fsat.$} The y-axis shows the fraction of galaxies that are not centrals, plotted as a function of stellar mass $\mstar.$ Different curves show results for three different choices for the treatment of disrupted subhalos, as indicated in the legend and described in the text of the appendix. 
}
\label{fig:orphan_satellite_fractions}
\end{figure}

@@

%-----------------------------------------------------------------------------------------------------
